### 2014-06-20 dicook/map.Rmd
got nice map, even with inserts

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(rworldmap)
```

@@

```{r maps, fig.width=12, fig.height=7}
# Extract map polygons for modern world
world <- getMap(resolution = "low")
library(plyr)
world.polys <- extractPolygons(world)
detach("package:plyr")
# Subset data
student2012.sub <- student2012[, c(1:7, 500:550)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$name <- as.character(student2012.sub$name)
# Check mismatches of names
unique(anti_join(student2012.sub, world.polys)[1])
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"

# Only need one of the plausible values, checked they are effectively identical
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$PV1MACC <- as.numeric(student2012.sub$PV1MACC)
student2012.sub$PV1MACQ <- as.numeric(student2012.sub$PV1MACQ)
student2012.sub$PV1MACS <- as.numeric(student2012.sub$PV1MACS)
student2012.sub$PV1MACU <- as.numeric(student2012.sub$PV1MACU)
student2012.sub$PV1MAPE <- as.numeric(student2012.sub$PV1MAPE)
student2012.sub$PV1MAPF <- as.numeric(student2012.sub$PV1MAPF)
student2012.sub$PV1MAPI <- as.numeric(student2012.sub$PV1MAPI)
student2012.sub.math <- summarise(group_by(student2012.sub[,c(1,seq(9,48,5))], name), math=mean(PV1MATH), mCC=mean(PV1MACC), 
                                  mCQ=mean(PV1MACQ), mCS=mean(PV1MACS), mCU=mean(PV1MACU), mPE=mean(PV1MAPE), 
                                  mPF=mean(PV1MAPF), mPI=mean(PV1MAPI))
#pairs(student2012.sub.math[,-1])

@@

# Join to get missings for countries that are not measured
#student2012.sub.map <- merge(student2012.sub.math, world.polys, all.y=TRUE)
#qplot(X1, X2, order=order, group=group, data=student2012.sub.map, geom="polygon", fill=math, colour=I("grey70")) + 
  #coord_map(xlim=c(-195, 185), ylim=c(-150, 95)) + # Having trouble getting coord_map to not cut off polygons weirdly
#  new_theme_empty + theme(legend.position="none")
```

>>>>

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(rworldmap)
library (grid)  	
library (scales)	
```

@@

```{r maps, fig.width=12, fig.height=7}
# Extract map polygons for modern world
world <- getMap(resolution = "low")
library(plyr)
world.polys <- extractPolygons(world)
detach("package:plyr")
# Subset data
student2012.sub <- student2012[, c(1:7, 500:550)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$name <- as.character(student2012.sub$name)
# Check mismatches of names
# unique(anti_join(student2012.sub, world.polys)[1])
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"

# Only need one of the plausible values, checked they are effectively identical
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$PV1MACC <- as.numeric(student2012.sub$PV1MACC)
student2012.sub$PV1MACQ <- as.numeric(student2012.sub$PV1MACQ)
student2012.sub$PV1MACS <- as.numeric(student2012.sub$PV1MACS)
student2012.sub$PV1MACU <- as.numeric(student2012.sub$PV1MACU)
student2012.sub$PV1MAPE <- as.numeric(student2012.sub$PV1MAPE)
student2012.sub$PV1MAPF <- as.numeric(student2012.sub$PV1MAPF)
student2012.sub$PV1MAPI <- as.numeric(student2012.sub$PV1MAPI)
student2012.sub.math <- summarise(group_by(student2012.sub[,c(1,seq(9,48,5))], name), math=mean(PV1MATH), mCC=mean(PV1MACC), 
                                  mCQ=mean(PV1MACQ), mCS=mean(PV1MACS), mCU=mean(PV1MACU), mPE=mean(PV1MAPE), 
                                  mPF=mean(PV1MAPF), mPI=mean(PV1MAPI))
colnames(student2012.sub.math)[-c(1:2)] <- c("Change", "Quantity", "Spatial", "Data", "Employ", "Formulate", "Interpret")

@@

# Now try to do an insert
# Note China is represented just by Shanghai
student2012.sub.math$name <- factor(student2012.sub.math$name, 
      levels=student2012.sub.math$name[order(student2012.sub.math$math)])
p1 <- ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey70")) + 
  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=math)) +
  new_theme_empty + theme(legend.position="none")
p2 <- qplot(name, math, data=student2012.sub.math, colour=math, ylab="Math Score", xlab="") + coord_flip() + 
  theme(legend.position="none")
p2 = ggplotGrob(p2)  			
p1 + annotation_custom(grob = p2, xmin = -40, xmax = 80, ymin = -110, ymax = 10)
```

```{r pairs, fig.width=12, fig.height=12}
library(YaleToolkit)
gpairs(student2012.sub.math[,-1])
# Should do a PCA, to look at what countries do better on what types of math skills
```
